---
title: "Assignment4"
author: "Whytne Stevens"
date: "9/24/2020"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
library(wesanderson)
library(viridis)
```


```{r load data, results='hide'}
person_data_new2 <- read.csv("persondatanew.csv")
```

# Regression Model for PINCP Variable
```{r}
model <- lm(PINCP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + POVPIP, 
            data = person_data_new2)

summary(model)
```
## Results
The multiple R-squared values is 0.3175, Predicts about 32% of this model
The coefficent estimate for WKHP is 1066.91
The coefficent estimate for POVPIP is 131.88
The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is -12571.06
The coefficent estimate for COW_labelFederal government employee is 84236.21 
The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is -11026.90
The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is 23195.88
The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is 5081.11
The coefficent estimate for COW_labelState government employee is -3451.12
The coefficent estimate for COW_labelWorking without pay in family business or farm is 7494.61
The coefficent estimate for HHL_labelEnglish only is 6423.48
The coefficent estimate for HHL_labelN/A (GQ/vacant)is 14286.91
The coefficent estimate for HHL_labelOther Indo-European languages is 25831.83
The coefficent estimate for HHL_labelOther language is 196.67
The coefficent estimate for HHL_labelSpanish is 7466.24
The coefficent estimate for ENG_labelNot at all is -14801.04
The coefficent estimate for ENG_labelNot well is -4002.39
The coefficent estimate for ENG_labelVery well is 3197.87
The coefficent estimate for ENG_labelWell is -10545.02
The coefficent estimate for FS_labelYes is -3615.81



# Regression Model for WKHP Variable
```{r}
model2 <- lm(WKHP ~ COW_label + HHL_label + ENG_label + FS_label + PINCP + POVPIP, 
            data = person_data_new2)

summary(model2)
```
## Results
The multiple R-squared values is 0.3175, Predicts about 32% of this model
The coefficent estimate for PINCP is 1066.91
The coefficent estimate for POVPIP is 131.88
The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is -12571.06
The coefficent estimate for COW_labelFederal government employee is 84236.21 
The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is -11026.90
The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is 23195.88
The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is 5081.11
The coefficent estimate for COW_labelState government employee is -3451.12
The coefficent estimate for COW_labelWorking without pay in family business or farm is 7494.61
The coefficent estimate for HHL_labelEnglish only is 6423.48
The coefficent estimate for HHL_labelN/A (GQ/vacant)is 14286.91
The coefficent estimate for HHL_labelOther Indo-European languages is 25831.83
The coefficent estimate for HHL_labelOther language is 196.67
The coefficent estimate for HHL_labelSpanish is 7466.24
The coefficent estimate for ENG_labelNot at all is -14801.04
The coefficent estimate for ENG_labelNot well is -4002.39
The coefficent estimate for ENG_labelVery well is 3197.87
The coefficent estimate for ENG_labelWell is -10545.02
The coefficent estimate for FS_labelYes is -3615.81
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for

# Regression Model for POVPIP Variable
```{r}
model3 <- lm(POVPIP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + PINCP, 
            data = person_data_new2)

summary(model3)
```
## Results
The multiple R-squared values is 0.3175, Predicts about 32% of this model
The coefficent estimate for WKHP is 1066.91
The coefficent estimate for POVPIP is 131.88
The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is -12571.06
The coefficent estimate for COW_labelFederal government employee is 84236.21 
The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is -11026.90
The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is 23195.88
The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is 5081.11
The coefficent estimate for COW_labelState government employee is -3451.12
The coefficent estimate for COW_labelWorking without pay in family business or farm is 7494.61
The coefficent estimate for HHL_labelEnglish only is 6423.48
The coefficent estimate for HHL_labelN/A (GQ/vacant)is 14286.91
The coefficent estimate for HHL_labelOther Indo-European languages is 25831.83
The coefficent estimate for HHL_labelOther language is 196.67
The coefficent estimate for HHL_labelSpanish is 7466.24
The coefficent estimate for ENG_labelNot at all is -14801.04
The coefficent estimate for ENG_labelNot well is -4002.39
The coefficent estimate for ENG_labelVery well is 3197.87
The coefficent estimate for ENG_labelWell is -10545.02
The coefficent estimate for FS_labelYes is -3615.81
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for
The coefficent estimate for














