---
title: "Assignment4"
author: "Whytne Stevens"
date: "9/24/2020"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
library(wesanderson)
library(viridis)
```


```{r load data, results='hide'}
person_data_new2 <- read.csv("persondatanew.csv")
```

# Regression Model for PINCP Variable
```{r}
model <- lm(PINCP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + POVPIP, 
            data = person_data_new2)

summary(model)
```
## Results
The multiple R-squared values is 0.3175, Predicts about 32% of this model

The coefficent estimate for WKHP is 1066.91

The coefficent estimate for POVPIP is 131.88

The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is -12571.06

The coefficent estimate for COW_labelFederal government employee is 84236.21 

The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is -11026.90

The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is 23195.88

The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is 5081.11

The coefficent estimate for COW_labelState government employee is -3451.12

The coefficent estimate for COW_labelWorking without pay in family business or farm is 7494.61

The coefficent estimate for HHL_labelEnglish only is 6423.48

The coefficent estimate for HHL_labelN/A (GQ/vacant)is 14286.91

The coefficent estimate for HHL_labelOther Indo-European languages is 25831.83

The coefficent estimate for HHL_labelOther language is 196.67

The coefficent estimate for HHL_labelSpanish is 7466.24

The coefficent estimate for ENG_labelNot at all is -14801.04

The coefficent estimate for ENG_labelNot well is -4002.39

The coefficent estimate for ENG_labelVery well is 3197.87

The coefficent estimate for ENG_labelWell is -10545.02

The coefficent estimate for FS_labelYes is -3615.81




# Regression Model for WKHP Variable
```{r}
model2 <- lm(WKHP ~ COW_label + HHL_label + ENG_label + FS_label + PINCP + POVPIP, 
            data = person_data_new2)

summary(model2)
```
## Results
The multiple R-squared values is 0.128, Predicts about 13% of this model

The coefficent estimate for PINCP is 7.485e-05

The coefficent estimate for POVPIP is 7.085e-03

The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is -3.318e+00

The coefficent estimate for COW_labelFederal government employee is -5.833e+00

The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is -5.632e-01

The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is -1.667e+00

The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is -1.941e+00

The coefficent estimate for COW_labelState government employee is -8.710e-02

The coefficent estimate for COW_labelWorking without pay in family business or farm is -1.055e+01 

The coefficent estimate for HHL_labelEnglish only is 4.067e-01

The coefficent estimate for HHL_labelN/A (GQ/vacant) is -3.375e+00 

The coefficent estimate for HHL_labelOther Indo-European languages is -1.628e+00

The coefficent estimate for HHL_labelOther language is -2.844e+00

The coefficent estimate for HHL_labelSpanish is -9.581e-01 

The coefficent estimate for ENG_labelNot at all is 5.788e+00 

The coefficent estimate for ENG_labelNot well is 5.402e+00

The coefficent estimate for ENG_labelVery well is 1.182e+00

The coefficent estimate for ENG_labelWell is 4.042e+00

The coefficent estimate for FS_labelYes is 8.922e-01


# Regression Model for POVPIP Variable
```{r}
model3 <- lm(POVPIP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + PINCP, 
            data = person_data_new2)

summary(model3)
```
## Results
The multiple R-squared values is 0.3523, Predicts about 35% of this model

The coefficent estimate for WKHP is 7.181e-01

The coefficent estimate for PINCP is 9.376e-04

The coefficent estimate for COW_labelEmployee of a private not-for-profit, tax-exempt, or charitable organization is 6.709e+01

The coefficent estimate for COW_labelFederal government employee is 1.116e+01 

The coefficent estimate for COW_labelLocal government employee (city, county, etc.) is 4.371e+01

The coefficent estimate for COW_labelSelf-employed in own incorporated business, professional practice or farm is -1.619e+01

The coefficent estimate for COW_labelSelf-employed in own not incorporated business, professional practice, or farm is -4.286e+01

The coefficent estimate for COW_labelState government employee is -1.202e+01 

The coefficent estimate for COW_labelWorking without pay in family business or farm is 1.347e+02 

The coefficent estimate for HHL_labelEnglish only is -3.297e+01

The coefficent estimate for HHL_labelN/A (GQ/vacant) is -2.936e+02

The coefficent estimate for HHL_labelOther Indo-European languages is -2.656e+01 

The coefficent estimate for HHL_labelOther language is -1.343e+01

The coefficent estimate for HHL_labelSpanish is -6.062e+01

The coefficent estimate for ENG_labelNot at all is -9.209e+01

The coefficent estimate for ENG_labelNot well is -1.085e+02

The coefficent estimate for ENG_labelVery well is -2.487e+01

The coefficent estimate for ENG_labelWell is -4.394e+01

The coefficent estimate for FS_labelYes is -8.173e+01



