---
title: "Assignment 1 and 2 - Variable Changes"
author: "Whytne Stevens"
date: "9/19/2020"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---
# Assignment 1 and 2 - Variable Changes
While working on assignment 3 I realized I needed to change some of my variables due to overly detailed variables that were making my analysis more complex.I still am interested in looking at whether there's a connection between one's profession, English language proficiency,household language and their income and income to poverty ratio. I stll narrowed down my analysis to person level data for Dallas County, Texas  from Public Use Microdata Sample (PUMAs) provided by the 2018 1 year American Community Survey. I have selected the following variables to explore this question:


- Class of Worker (COW) (categorical)

- English ability (ENG) (categorical)

- Household Language (HHL) (categorical)

- Food Stamps (FS)(Categorical)

- Total Person's Income (PINCP) (continuous)

- Hours worked per week (WKHP) (continuous)

- Income to Poverty Ratio (POVPIP) (continuous)

- Adjustment factor for income and earnings dollar amounts (6 implied decimal places) (ADJINC)(Continuous)*

*used for PINCP Variable



## Variables I added and took away
In place of the specific occupation variable, I used class of worker since this simplifies the occupations to the type of employee a person is as opposed to their particular occupation, therefore simplifying my analysis added food stamps to better understand who might be receiving public assistance of some sort since public assistance is usually used as an indicator of some type of financial hardship if not poverty. I also added household language as I wanted to see if there are some correlations there as it relates to languages and income/poverty. As for the variables I took away, race, sex, and specific occupation weren't necessarily adding to my analysis and if anything were complicating it further, particularly the specific occupation and race variables.

# Set Up and Data Output
I also set up everything below as in Assignment 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
```

```{r load person-level microdata variables}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```

```{r load ACS area variables}
area_vars_2018 <- load_variables(2018, "acs1")
```

```{r message=FALSE, results='hide'}
dallas_county <- c("02301", "02302", "02303", "02304", "02308", "02317", "02318", "02319", "02320", "02321", "02322")
```

```{r load person-level data, results= 'hide'}
person_data_new <- get_pums(variables = c("PUMA",
                                      "COW",
                                      "HHL",
                                      "ENG",
                                      "FS",
                                      "PINCP", 
                                      "WKHP", 
                                      "POVPIP",
                                      "ADJINC"),
                        state = "TX",
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>% 
  filter(PUMA == dallas_county,
         PINCP > 0,
         WKHP > 0,
         POVPIP > 0) %>%
  select(COW_label, HHL_label, ENG_label, FS_label, PINCP, WKHP, POVPIP)
```

```{r load person_data_new}
 head(person_data_new, 1)
 tail(person_data_new, 596)
```
## Saving Data
Lastly, I saved my data to a csv file:

```{r write_csv}
write_csv(person_data_new, "persondatanew.csv")
```



# Part two


```{r read_csv}
person_data_new <- read_csv("persondatanew.csv")
```


# Distributions of my Continuous Variables
For each of my continuous variables (total person's income, hours worked per week, and income to poverty ratio) below, I calculated the sample men, median, standard deviation, and interquartile ranges. I also calculated the 95-percent confidence interval for the mean of each of these variables and created a histogram to show that distribution


## Total person's income

```{r}
PINCP_summary2 <- summary(person_data_new$PINCP)

PINCP_summary2
```
```{r}
paste("The sample mean for total person's income is",
      prettyNum(mean(person_data_new$PINCP), digits = 1), "USD.")
paste("The sample median for total person's income is",
      prettyNum(median(person_data_new$PINCP), digits = 1), "USD.")  
paste("The sample standard deviation for total person's income is",
      prettyNum(sd(person_data_new$PINCP), digits = 1), "USD.")
paste("The sample interquartile range for total person's income is",
      quantile(person_data_new$PINCP)["25%"], "to", quantile(person_data_new$PINCP)["75%"], "USD.")
```


```{r}
conf_int_pincp2 <- t.test(person_data_new$PINCP)

conf_int_pincp2
```

```{r}
paste("The 95-percent confidence interval for total person's income is",
      prettyNum(conf_int_pincp2$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_pincp2$conf.int[2], digits = 1), "USD.")
```


```{r}
hist_pincp2 <-ggplot(person_data_new, aes(x = PINCP)) +
  geom_histogram()

hist_pincp2
```

```{r}
hist_pincp2 + 
  theme_solarized_2() +
  scale_x_continuous(name = "Total person's income (USD)") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 490000, y = 150, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_pincp2$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_pincp2$conf.int[2], digits = 1),
                         "USD.",
                         "\nSample mean:", 
                         prettyNum(mean(PINCP_summary2), digits = 1), "USD.",
                         "\nSample median:",
                         prettyNum(median(PINCP_summary2), digits = 1), "USD.",
                         "\nSample standard deviation:",
                         prettyNum(sd(PINCP_summary2), digits = 1), "USD.", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(PINCP_summary2)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(PINCP_summary2)["75%"], digits = 1),
                         "USD."),
           hjust = 1, vjust = 1) 
```



## Hours worked per week
```{r}
WKHP_summary2 <- summary(person_data_new$WKHP)

WKHP_summary2
```
```{r}
paste("The sample mean for hours worked per week is",
      prettyNum(mean(person_data_new$WKHP), digits = 1), "hours per week.")
paste("The sample median for hours worked per week is",
      prettyNum(median(person_data_new$WKHP), digits = 1), "hours per week.")  
paste("The sample standard deviation for hours worked per week is",
      prettyNum(sd(person_data_new$WKHP), digits = 1), "hours per week.")
paste("The sample interquartile range for hours worked per week is",
      quantile(person_data_new$WKHP)["25%"], "to", quantile(person_data_new$WKHP)["75%"], "hours per week.")
```


```{r}
conf_int_wkhp2 <- t.test(person_data_new$WKHP)

conf_int_wkhp2
```

```{r}
paste("The 95-percent confidence interval for hours worked per week  is",
      prettyNum(conf_int_wkhp2$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_wkhp2$conf.int[2], digits = 1), "hours per week.")
```

```{r}
hist_wkhp2 <- ggplot(person_data_new, aes(x = WKHP)) +
  geom_histogram()
hist_wkhp2
```

```{r}
hist_wkhp2 + 
  theme_solarized_2() +
  scale_x_continuous(name = "Hours worked per week") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 100, y = 275, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_wkhp2$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_wkhp2$conf.int[2], digits = 1),
                         "hours per week.",
                         "\nSample mean:", 
                         prettyNum(mean(WKHP_summary2), digits = 1), "hours per week.",
                         "\nSample median:",
                         prettyNum(median(WKHP_summary2), digits = 1), "hours per week.",
                         "\nSample standard deviation:",
                         prettyNum(sd(WKHP_summary2), digits = 1), "hours per week.", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(WKHP_summary2)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(WKHP_summary2)["75%"], digits = 1),
                         "hours per week."),
           hjust = 1, vjust = 1) 
```

## Income to poverty ratio
```{r}
POVPIP_summary2 <- summary(person_data_new$POVPIP)

POVPIP_summary2
```

```{r}
paste("The sample mean for income to poverty ratio is",
      prettyNum(mean(person_data_new$POVPIP), digits = 1), ".")
paste("The sample median for income to poverty ratio is",
      prettyNum(median(person_data_new$POVPIP), digits = 1), ".")  
paste("The sample standard deviation for income to poverty ratio is",
      prettyNum(sd(person_data_new$POVPIP), digits = 1), ".")
paste("The sample interquartile range for income to poverty ratio is",
      quantile(person_data_new$POVPIP)["25%"], "to", quantile(person_data_new$POVPIP)["75%"], ".")
```

```{r}
conf_int_povpip2 <- t.test(person_data_new$POVPIP)

conf_int_povpip2
```

```{r}
paste("The 95-percent confidence interval for income to poverty ratio is",
      prettyNum(conf_int_povpip2$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_povpip2$conf.int[2], digits = 1), ".")
```

```{r}
hist_povpip2 <- ggplot(person_data_new, aes(x = POVPIP)) +
  geom_histogram()
hist_povpip2
```


```{r}
hist_povpip2 + 
  theme_solarized_2() +
  scale_x_continuous(name = "Income to poverty ratio") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 100, y = 200, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_povpip2$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_povpip2$conf.int[2], digits = 1),
                         "hours per week.",
                         "\nSample mean:", 
                         prettyNum(mean(POVPIP_summary2), digits = 1), ".",
                         "\nSample median:",
                         prettyNum(median(POVPIP_summary2), digits = 1), ".",
                         "\nSample standard deviation:",
                         prettyNum(sd(POVPIP_summary2), digits = 1), ".", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(POVPIP_summary2)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(POVPIP_summary2)["75%"], digits = 1),
                         "."),
           hjust = 0, vjust = 1) 
```



# Proportions of my Categorial Variables
As for my categorical variables (class of worker, household language, English language proficiency, and whether or not someone receives food stamps) below, I calculated the distribution of each by looking at the number observation in each variable category, converted the number of these observations to proportions, and calculated the 95-percent confidence interval for each of these proportions as well.

## Class of Worker (COW)

```{r}
unique(person_data_new$COW_label)
```

```{r}
table(person_data_new$COW_label)
knitr::kable(table(person_data_new$COW_label), caption = "Frequency Counts for COW Variable")
```

```{r}
table(person_data_new$COW_label) / sum(table(person_data_new$COW_label))
```

```{r}
mean(person_data_new$COW_label == "Employee of a private not-for-profit, tax-exempt, or charitable organization")
```

```{r}
t.test(person_data_new$COW_label == "Employee of a private not-for-profit, tax-exempt, or charitable organization")
```

```{r}
tenures1new <- unique(person_data_new$COW_label)
tenures1new
```



```{r}
forprofitemp <- t.test(person_data_new$COW_label == tenures1new[1])
localgovemp <- t.test(person_data_new$COW_label == tenures1new[2])
nonprofitemp <- t.test(person_data_new$COW_label == tenures1new[3])
selfemp_inc <-  t.test(person_data_new$COW_label == tenures1new[4])
selfemp_notinc <-  t.test(person_data_new$COW_label == tenures1new[5])
stategovemp <- t.test(person_data_new$COW_label == tenures1new[6])
fedgovemp <-  t.test(person_data_new$COW_label == tenures1new[7])
worknopay <-  t.test(person_data_new$COW_label == tenures1new[8])
shares <- tibble(Tenure = c("Employee of a private for-profit company or business, or of an individual, for wages, salary, or commissions",
                            "Local government employee (city, county, etc.)",                                                          
                            "Employee of a private not-for-profit, tax-exempt, or charitable organization",                               
                            "Self-employed in own not incorporated business, professional practice, or farm",                            
                            "Self-employed in own incorporated business, professional practice or farm",                                   
                            "State government employee",                                                                                   
                            "Federal government employee",                                                                                
                            "Working without pay in family business or farm"),
                 `Share` = c(forprofitemp$estimate, 
                             localgovemp$estimate,
                             nonprofitemp$estimate,
                             selfemp_inc$estimate,
                             selfemp_notinc$estimate,
                             stategovemp$estimate,
                             fedgovemp$estimate,
                             worknopay$estimate),
                 Low = c(forprofitemp$conf.int[1],
                         localgovemp$conf.int[1],
                         nonprofitemp$conf.int[1],
                         selfemp_inc$conf.int[1],
                         selfemp_notinc$conf.int[1],
                         stategovemp$conf.int[1],
                         fedgovemp$conf.int[1],
                         worknopay$conf.int[1]),
                 High = c(forprofitemp$conf.int[2],
                         localgovemp$conf.int[2],
                         nonprofitemp$conf.int[2],
                         selfemp_inc$conf.int[2],
                         selfemp_notinc$conf.int[2],
                         stategovemp$conf.int[2],
                         fedgovemp$conf.int[2],
                         worknopay$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for COW variable")
```


```{r load tenures1new}
ggplot(shares, aes(x = Tenure, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity") +
  geom_errorbar(width = 0.5) +
  theme_solarized_2() +
  theme(axis.text.x = element_text(angle = 5)) +
  scale_x_discrete(name = "Class of Worker",
                   labels = c("Employee \nof a private \nfor-profit \ncompany",
                  "Employee \nof a private \nnot-for-profit \norganization", 
                   "Federal \ngovernment \nemployee",
                   "Local \ngovernment \nemployee",
                   "Self-employed \nin own \ninc. \nbusiness",
                   "Self-employed \nin own \nnot inc. \nbusiness",
                   "State \ngovernment \nemployee",
                  "Working \nw/o pay in \nfamily business \nor farm")) +
  scale_y_continuous(name = "Share of population (error bars represent\n 95-percent confidence interval)",
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8),
                     labels = c("0", "10%", "20%", "30%", "40%", "50%", "60%", "70%", "80%"))
```



## Household Language (HHL)

```{r}
unique(person_data_new$HHL_label)
```

```{r}
table(person_data_new$HHL_label)
knitr::kable(table(person_data_new$HHL_label), caption = "Frequency Counts for HHL Variable")
```

```{r}
table(person_data_new$HHL_label) / sum(table(person_data_new$HHL_label))
```

```{r}
mean(person_data_new$HHL_label == "Asian and Pacific Island languages")
```

```{r}
t.test(person_data_new$HHL_label == "Asian and Pacific Island languages")
```

```{r}
tenures2new <- unique(person_data_new$HHL_label)
tenures2new
```



```{r}
spanish <- t.test(person_data_new$HHL_label == tenures2new[1])
english <- t.test(person_data_new$HHL_label == tenures2new[2])
other_indo_european_lang <- t.test(person_data_new$HHL_label == tenures2new[3])
asian_pi_lang <- t.test(person_data_new$HHL_label == tenures2new[4])
other_lang <- t.test(person_data_new$HHL_label == tenures2new[5])
na_vacant <- t.test(person_data_new$HHL_label == tenures2new[6])
shares <- tibble(Tenure = c("Spanish",
                            "English only",
                            "Other Indo-European languages",
                            "Asian and Pacific Island languages",
                            "Other language",
                            "N/A (GQ/vacant)"),
                 `Share` = c(spanish$estimate,
                             english$estimate,
                             other_indo_european_lang$estimate,
                             asian_pi_lang$estimate,
                             other_lang$estimate,
                             na_vacant$estimate),
                 Low = c(spanish$conf.int[1],
                         english$conf.int[1],
                         other_indo_european_lang$conf.int[1],
                         asian_pi_lang$conf.int[1],
                         other_lang$conf.int[1],
                         na_vacant$conf.int[1]),
                 High = c(spanish$conf.int[2],
                         english$conf.int[2],
                         other_indo_european_lang$conf.int[2],
                         asian_pi_lang$conf.int[2],
                         other_lang$conf.int[2],
                         na_vacant$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for HHL variable")
```


```{r load tenures2new}
ggplot(shares, aes(x = Tenure, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity") +
  geom_errorbar(width = 0.5) +
  theme_solarized_2() +
  theme(axis.text.x = element_text(angle = 0)) +
  scale_x_discrete(name = "Houshold Language",
                   labels = c("Spanish",
                            "English only",
                            "Other Indo-\nEuropean \nlanguages",
                            "Asian and \nPacific Island \nlanguages",
                            "Other language",
                            "N/A \n(GQ/vacant)")) +
  scale_y_continuous(name = "Share of population (error bars represent\n 95-percent confidence interval)",
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     labels = c("0", "10%", "20%", "30%", "40%", "50%"))
```

## Food Stamps (FS)

```{r}
unique(person_data_new$FS_label)
```

```{r}
table(person_data_new$FS_label)
knitr::kable(table(person_data_new$FS_label), caption = "Frequency Counts for FS Variable")
```

```{r}
table(person_data_new$FS_label) / sum(table(person_data_new$FS_label))
```


```{r}
mean(person_data_new$FS_label == "No")
```

```{r}
t.test(person_data_new$FS_label == "No")
```

```{r}
tenures3new <- unique(person_data_new$FS_label)
tenures3new
```


```{r}
no <- t.test(person_data_new$FS_label == tenures3new[1])
yes <- t.test(person_data_new$FS_label == tenures3new[2])
shares <- tibble(Tenure = c("No", 
                            "Yes"),
                 `Share` = c(no$estimate, 
                             yes$estimate),
                 Low = c(no$conf.int[1],
                         yes$conf.int[1]),
                 High = c(no$conf.int[2],
                          yes$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for FS variable")
```

```{r load tenures3new}
ggplot(shares, aes(x = Tenure, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity") +
  geom_errorbar(width = 0.5) +
  theme_solarized_2() +
  scale_x_discrete(labels = c("No", 
                            "Yes")) +
  scale_y_continuous(name = "Share of population \nreceiving Food Stamps (error bars represent\n 95-percent confidence interval)",
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     labels = c("0", "10%", "20%", "30%", "40%", "50%"))
```





## English language proficiency

```{r}
unique(person_data_new$ENG_label)
```

```{r}
table(person_data_new$ENG_label)
knitr::kable(table(person_data_new$ENG_label), caption = "Frequency Counts for ENG Variable")
```

```{r}
table(person_data_new$ENG_label) / sum(table(person_data_new$ENG_label))
```

```{r}
mean(person_data_new$ENG_label == "Not well")
```

```{r}
t.test(person_data_new$ENG_label == "Not well")
```


```{r}
tenures4new <- unique(person_data_new$ENG_label)
tenures4new
```



```{r}
well <- t.test(person_data_new$ENG_label == tenures4new[1])
lessthan5years_onlyspeakseng <- t.test(person_data_new$ENG_label == tenures4new[2])
very_well <- t.test(person_data_new$ENG_label == tenures4new[3])
not_at_all <-  t.test(person_data_new$ENG_label == tenures4new[4])
not_well <-  t.test(person_data_new$ENG_label == tenures4new[5])
shares <- tibble(Tenure = c("Well", 
                            "N/A (less than 5 years old/speaks only English)", 
                            "Very well",
                            "Not at all",
                            "Not well"),
                 `Share` = c(well$estimate, 
                             lessthan5years_onlyspeakseng$estimate,
                             very_well$estimate,
                             not_at_all$estimate,
                             not_well$estimate),
                 Low = c(well$conf.int[1],
                         lessthan5years_onlyspeakseng$conf.int[1],
                         very_well$conf.int[1],
                         not_at_all$conf.int[1],
                         not_well$conf.int[1]),
                 High = c(well$conf.int[2],
                         lessthan5years_onlyspeakseng$conf.int[2],
                         very_well$conf.int[2],
                         not_at_all$conf.int[2],
                         not_well$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for ENG variable")
```

```{r load tenures4new}
ggplot(shares, aes(x = Tenure, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity") +
  geom_errorbar(width = 0.5) +
  theme_solarized_2() +
  scale_x_discrete(labels = c("Well", 
                            "N/A \n(less than 5 years old/\nspeaks only English)", 
                            "Very well",
                            "Not at all",
                            "Not well")) +
  scale_y_continuous(name = "Share of population (error bars represent\n 95-percent confidence interval)",
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     labels = c("0", "10%", "20%", "30%", "40%", "50%"))
```


