---
title: "Assignment4"
author: "Whytne Stevens"
date: "9/24/2020"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
library(wesanderson)
library(viridis)
```


```{r load data, results='hide'}
person_data_new2 <- read.csv("persondatanew.csv") %>%
mutate(ENG_label = case_when(
    ENG_label=="N/A (less than 5 years old/speaks only English)"~"1N/A (less than 5 years old/speaks only English)",
    ENG_label=="Well"~"Well",
    ENG_label=="Very well"~"Very well",
    ENG_label=="Not well"~"Not well",
    ENG_label=="Not at all"~"Not at all"),
    HHL_label = case_when(
    HHL_label=="English only"~"1English only",
    HHL_label=="Asian and Pacific Island languages"~"Asian and Pacific Island languages",
    HHL_label=="Other Indo-European languages" ~ "Other Indo-European languages",
    HHL_label=="Other language" ~ "Other language",
    HHL_label=="Spanish" ~ "Spanish"),
    COW_label = case_when(
    COW_label=="Employee of a private for-profit company or business, or of an individual, for wages, salary, or commissions" ~ "1Employee of a private for-profit company/business",
    COW_label=="Employee of a private not-for-profit, tax-exempt, or charitable organization" ~ "Employee of a private not-for-profit organization",
    COW_label=="Federal government employee" ~ "Federal government employee",
    COW_label=="Local government employee (city, county, etc.)" ~ "Local government employee",
    COW_label=="State government employee" ~ "State government employee",
    COW_label=="Self-employed in own incorporated business, professional practice or farm"~"Self-employed in own incorporated business, professional practice or farm",
    COW_label=="Self-employed in own not incorporated business, professional practice, or farm" ~ "Self-employed in own not incorporated business, professional practice, or farm",
    COW_label=="Working without pay in family business or farm" ~ "Working without pay in family business or farm"),
    FS_label = case_when(
    FS_label=="No" ~ "1No",
    FS_label=="Yes" ~ "Yes"))
 

```

# Regression Model For Continuous Variables



# Regression Model for PINCP Variable
```{r}
model <- lm(PINCP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + POVPIP, 
            data = person_data_new2)
options(scipen = 999)
summary(model)
```
## Results
The multiple R-squared values is 0.3169, Predicts about 32% of this model

Strong and Significant
- COW_labelFederal government employee 84236.21
- WKHP 1066.91 
- POVPIP  131.88 

Weak
- COW_labelSelf-employed in own incorporated business, professional practice or farm  23195.88

Very Weak
- HHL_labelOther Indo-European languages 19408.35




# Regression Model for WKHP Variable
```{r}
model2 <- lm(WKHP ~ COW_label + HHL_label + ENG_label + FS_label + PINCP + POVPIP, 
            data = person_data_new2)
options(scipen = 999)
summary(model2)
```
## Results
The multiple R-squared values is 0.1272, Predicts about 13% of this model

Strong and Significant
- PINCP 0.00007485

Weak
- ENG_labelNot well 5.40207333

Very Weak
- POVPIP  0.00708539



# Regression Model for POVPIP Variable
```{r}
model3 <- lm(POVPIP ~ COW_label + HHL_label + ENG_label + FS_label + WKHP + PINCP, 
            data = person_data_new2)
options(scipen = 999)
summary(model3)
```
## Results
The multiple R-squared values is 0.3482, Predicts about 35% of this model

Strong and Significant
- ENG_labelNot well, -108.5138605
- FS_labelYes,  -81.7288664
- PINCP, 0.0009376

Significant
- COW_labelEmployee of a private not-for-profit organization, 67.0897929

Weak
- COW_labelLocal government employee,  43.7144380
- COW_labelSelf-employed in own not incorporated business, professional practice, or farm -42.8613915
- ENG_labelNot at all -92.0866650

Very Weak
- WKHP 0.7180711


