---
title: "Assignment2"
author: "Whytne Stevens"
date: "9/8/2020"
output: html_document
---
# Assignment 2
Continuing with the variables and data used in Assignment 1, I am now looking at the distributions and proportions of these variables, which are listed below:

Race (RAC3P) (categorical)

Sex (SEX) (categorical)

Standard Occupational Classification (SOCP) (categorical)

English ability (ENG) (categorical)

Language other than English spoken at home (LANX) (categorical)

Income (PINCP) (continuous)

Work hours per week (WKHP) (continuous)

Income-to-poverty ratio (POVPIP) (continuous)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r load libraries}
library(ggplot2)
library(tidycensus)
library(tidyverse)
library(ggthemes)
```




```{r load person-level microdata variables}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```




```{r load ACS area variables}
area_vars_2018 <- load_variables(2018, "acs1")
```




```{r message=FALSE, results='hide'}
dallas_county <- c("02301", "02302", "02303", "02304", "02308", "02317", "02318", "02319", "02320", "02321", "02322")
```




```{r load person-level data, results= 'hide'}
person_data <- get_pums(variables = c("PUMA",
                                      "RAC1P",
                                      "SEX",
                                      "SOCP",
                                      "LANX",
                                      "ENG", 
                                      "PINCP", 
                                      "WKHP", 
                                      "POVPIP"),
                        state = "TX",
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>% 
  mutate(SOCP = as.numeric(SOCP)) %>% 
  filter(PUMA == dallas_county,
         PINCP > 0,
         SOCP > 0,
         WKHP > 0,
         POVPIP > 0) %>%
  select(RAC1P_label, SEX_label, SOCP_label, ENG_label, LANX_label, PINCP, WKHP, POVPIP)
```


```{r read_csv}
person_data <- read_csv("assignmentonedata.csv")
```


# Distributions of my Continuous Variables
For each of my continuous variables (total person's income, hours worked per week, and income to poverty ratio) below, I calculated the sample men, median, standard deviation, and interquartile ranges. I also calculated the 95-percent confidence interval for the mean of each of these variables and created a histogram to show that distribution


## Total person's income

```{r}
PINCP_summary <- summary(person_data$PINCP)

PINCP_summary
```
```{r}
paste("The sample mean for total person's income is",
      prettyNum(mean(person_data$PINCP), digits = 1), "USD.")
paste("The sample median for total person's income is",
      prettyNum(median(person_data$PINCP), digits = 1), "USD.")  
paste("The sample standard deviation for total person's income is",
      prettyNum(sd(person_data$PINCP), digits = 1), "USD.")
paste("The sample interquartile range for total person's income is",
      quantile(person_data$PINCP)["25%"], "to", quantile(person_data$PINCP)["75%"], "USD.")
```


```{r}
conf_int_pincp <- t.test(person_data$PINCP)

conf_int_pincp
```

```{r}
paste("The 95-percent confidence interval for total person's income is",
      prettyNum(conf_int_pincp$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_pincp$conf.int[2], digits = 1), "USD.")
```


```{r}
hist_pincp <-ggplot(person_data, aes(x = PINCP)) +
  geom_histogram()

hist_pincp
```

```{r}
hist_pincp + 
  theme_solarized_2() +
  scale_x_continuous(name = "Total person's income (USD)") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 490000, y = 150, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_pincp$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_pincp$conf.int[2], digits = 1),
                         "USD.",
                         "\nSample mean:", 
                         prettyNum(mean(PINCP_summary), digits = 1), "USD.",
                         "\nSample median:",
                         prettyNum(median(PINCP_summary), digits = 1), "USD.",
                         "\nSample standard deviation:",
                         prettyNum(sd(PINCP_summary), digits = 1), "USD.", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(PINCP_summary)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(PINCP_summary)["75%"], digits = 1),
                         "USD."),
           hjust = 1, vjust = 1) 
```



## Hours worked per week
```{r}
WKHP_summary <- summary(person_data$WKHP)

WKHP_summary
```
```{r}
paste("The sample mean for hours worked per week is",
      prettyNum(mean(person_data$WKHP), digits = 1), "hours per week.")
paste("The sample median for hours worked per week is",
      prettyNum(median(person_data$WKHP), digits = 1), "hours per week.")  
paste("The sample standard deviation for hours worked per week is",
      prettyNum(sd(person_data$WKHP), digits = 1), "hours per week.")
paste("The sample interquartile range for hours worked per week is",
      quantile(person_data$WKHP)["25%"], "to", quantile(person_data$WKHP)["75%"], "hours per week.")
```


```{r}
conf_int_wkhp <- t.test(person_data$WKHP)

conf_int_wkhp
```

```{r}
paste("The 95-percent confidence interval for hours worked per week  is",
      prettyNum(conf_int_wkhp$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_wkhp$conf.int[2], digits = 1), "hours per week.")
```

```{r}
hist_wkhp <- ggplot(person_data, aes(x = WKHP)) +
  geom_histogram()
hist_wkhp
```

```{r}
hist_wkhp + 
  theme_solarized_2() +
  scale_x_continuous(name = "Hours worked per week") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 100, y = 275, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_wkhp$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_wkhp$conf.int[2], digits = 1),
                         "hours per week.",
                         "\nSample mean:", 
                         prettyNum(mean(WKHP_summary), digits = 1), "hours per week.",
                         "\nSample median:",
                         prettyNum(median(WKHP_summary), digits = 1), "hours per week.",
                         "\nSample standard deviation:",
                         prettyNum(sd(WKHP_summary), digits = 1), "hours per week.", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(WKHP_summary)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(WKHP_summary)["75%"], digits = 1),
                         "hours per week."),
           hjust = 1, vjust = 1) 
```

## Income to poverty ratio
```{r}
POVPIP_summary <- summary(person_data$POVPIP)

POVPIP_summary
```

```{r}
paste("The sample mean for income to poverty ratio is",
      prettyNum(mean(person_data$POVPIP), digits = 1), ".")
paste("The sample median for income to poverty ratio is",
      prettyNum(median(person_data$POVPIP), digits = 1), ".")  
paste("The sample standard deviation for income to poverty ratio is",
      prettyNum(sd(person_data$POVPIP), digits = 1), ".")
paste("The sample interquartile range for income to poverty ratio is",
      quantile(person_data$POVPIP)["25%"], "to", quantile(person_data$POVPIP)["75%"], ".")
```

```{r}
conf_int_povpip <- t.test(person_data$POVPIP)

conf_int_povpip
```

```{r}
paste("The 95-percent confidence interval for income to poverty ratio is",
      prettyNum(conf_int_povpip$conf.int[1], digits = 1), "to",
      prettyNum(conf_int_povpip$conf.int[2], digits = 1), ".")
```

```{r}
hist_povpip <- ggplot(person_data, aes(x = POVPIP)) +
  geom_histogram()
hist_povpip
```


```{r}
hist_povpip + 
  theme_solarized_2() +
  scale_x_continuous(name = "Income to poverty ratio") +
  scale_y_continuous(name = "Number of people in sample") +
  annotate("text", x = 100, y = 200, size = 3, 
           label = paste("Population mean (95% confidence):",
                         prettyNum(conf_int_povpip$conf.int[1], digits = 1),
                         "to",
                         prettyNum(conf_int_povpip$conf.int[2], digits = 1),
                         "hours per week.",
                         "\nSample mean:", 
                         prettyNum(mean(POVPIP_summary), digits = 1), ".",
                         "\nSample median:",
                         prettyNum(median(POVPIP_summary), digits = 1), ".",
                         "\nSample standard deviation:",
                         prettyNum(sd(POVPIP_summary), digits = 1), ".", 
                         "\nSample interquartile range:",
                         prettyNum(quantile(POVPIP_summary)["25%"], digits = 1),
                         "to",
                         prettyNum(quantile(POVPIP_summary)["75%"], digits = 1),
                         "."),
           hjust = 0, vjust = 1) 
```



# Proportions of my Categorial Variables
As for my categorical variables (race, sex, occupation, English language proficiency, and whether or not someone speaks a language besides English at home) below, I calculated the distribution of each by looking at the number observation in each variable category, converted the number of these observations to proportions, and calculated the 95-percent confidence interval for each of these proportions as well.

## Race

```{r}
unique(person_data$RAC1P_label)
```

```{r}
table(person_data$RAC1P_label)
knitr::kable(table(person_data$RAC1P_label), caption = "Frequency Counts for RAC1P Variable")
```

```{r}
table(person_data$RAC1P_label) / sum(table(person_data$RAC1P_label))
```

```{r}
mean(person_data$RAC1P_label == "Black or African American alone")
```

```{r}
t.test(person_data$RAC1P_label == "Black or African American alone")
```

```{r}
tenures1 <- unique(person_data$RAC1P_label)
tenures1
```



```{r}
white <- t.test(person_data$RAC1P_label == tenures1[1])
black <- t.test(person_data$RAC1P_label == tenures1[2])
asian <- t.test(person_data$RAC1P_label == tenures1[3])
two_or_more_race <-  t.test(person_data$RAC1P_label == tenures1[4])
some_other_race_alone <-  t.test(person_data$RAC1P_label == tenures1[5])
amer_ind_alone <- t.test(person_data$RAC1P_label == tenures1[6])
amer_ind_ala_native_tribes_spec_or_not_spec <-  t.test(person_data$RAC1P_label == tenures1[7])
nat_hawaiian_and_oth_pac_is_alone <-  t.test(person_data$RAC1P_label == tenures1[8])
shares <- tibble(Tenure = c("White alone", 
                            "Black or African American alone", 
                            "Asian alone",
                            "Two or More Races",
                            "Some Other Race alone",                                                                                                    
                            "American Indian alone",                                                                                                    
                            "American Indian and Alaska Native tribes specified; or American Indian or Alaska Native, not specified and no other races",
                            "Native Hawaiian and Other Pacific Islander alone"),
                 `Share` = c(white$estimate, 
                             black$estimate,
                             asian$estimate,
                             two_or_more_race$estimate,
                             some_other_race_alone$estimate,
                             amer_ind_alone$estimate,
                             amer_ind_ala_native_tribes_spec_or_not_spec$estimate,
                             nat_hawaiian_and_oth_pac_is_alone$estimate),
                 Low = c(white$conf.int[1],
                         black$conf.int[1],
                         asian$conf.int[1],
                         two_or_more_race$conf.int[1],
                         some_other_race_alone$conf.int[1],
                         amer_ind_alone$conf.int[1],
                         amer_ind_ala_native_tribes_spec_or_not_spec$conf.int[1],
                         nat_hawaiian_and_oth_pac_is_alone$conf.int[1]),
                 High = c(white$conf.int[2],
                         black$conf.int[2],
                         asian$conf.int[2],
                         two_or_more_race$conf.int[2],
                         some_other_race_alone$conf.int[2],
                         amer_ind_alone$conf.int[2],
                         amer_ind_ala_native_tribes_spec_or_not_spec$conf.int[2],
                         nat_hawaiian_and_oth_pac_is_alone$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for RAC1P variable")
```




## Sex

```{r}
unique(person_data$SEX_label)
```

```{r}
table(person_data$SEX_label)
knitr::kable(table(person_data$SEX_label), caption = "Frequency Counts for SEX Variable")
```

```{r}
table(person_data$SEX_label) / sum(table(person_data$SEX_label))
```

```{r}
mean(person_data$SEX_label == "Female")
```

```{r}
t.test(person_data$SEX_label == "Female")
```

```{r}
tenures2 <- unique(person_data$SEX_label)
tenures2
```



```{r}
female <- t.test(person_data$SEX_label == tenures2[1])
male <- t.test(person_data$SEX_label == tenures2[2])
shares <- tibble(Tenure = c("Female", 
                            "Male"),
                 `Share` = c(female$estimate, 
                             male$estimate),
                 Low = c(female$conf.int[1],
                         male$conf.int[1]),
                 High = c(female$conf.int[2],
                          male$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for SEX variable")
```



## Occupation

```{r}
unique(person_data$SOCP_label)
```

```{r}
table(person_data$SOCP_label)
knitr::kable(table(person_data$SOCP_label), caption = "Frequency Counts for SOCP Variable")
```

```{r}
table(person_data$SOCP_label) / sum(table(person_data$SOCP_label))
```


```{r}
mean(person_data$SOCP_label == "MGR-Social And Community Service Managers")
```

```{r}
t.test(person_data$SOCP_label == "MGR-Social And Community Service Managers")
```
Due to the number of occupations listed, I did not do a Proportions and 95-percent confidence intervals table for this variable

## Language other than English spoken at home

```{r}
unique(person_data$LANX_label)
```

```{r}
table(person_data$LANX_label)
knitr::kable(table(person_data$LANX_label), caption = "Frequency Counts for LANX Variable")
```

```{r}
table(person_data$LANX_label) / sum(table(person_data$LANX_label))
```

```{r}
mean(person_data$LANX_label == "Yes, speaks another language")
```

```{r}
t.test(person_data$LANX_label == "Yes, speaks another language")
```

```{r}
tenures3 <- unique(person_data$LANX_label)
tenures3
```



```{r}
yes <- t.test(person_data$LANX_label == tenures3[1])
no <- t.test(person_data$LANX_label == tenures3[2])
shares <- tibble(Tenure = c("Yes, speaks another language", 
                            "No, speaks only English"),
                 `Share` = c(yes$estimate, 
                             no$estimate),
                 Low = c(yes$conf.int[1],
                         no$conf.int[1]),
                 High = c(yes$conf.int[2],
                          no$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for LANX variable")
```



## English language proficiency

```{r}
unique(person_data$ENG_label)
```

```{r}
table(person_data$ENG_label)
knitr::kable(table(person_data$ENG_label), caption = "Frequency Counts for ENG Variable")
```

```{r}
table(person_data$ENG_label) / sum(table(person_data$ENG_label))
```

```{r}
mean(person_data$ENG_label == "Not well")
```

```{r}
t.test(person_data$ENG_label == "Not well")
```


```{r}
tenures4 <- unique(person_data$ENG_label)
tenures4
```



```{r}
well <- t.test(person_data$ENG_label == tenures4[1])
lessthan5years_onlyspeakseng <- t.test(person_data$ENG_label == tenures4[2])
very_well <- t.test(person_data$ENG_label == tenures4[3])
not_at_all <-  t.test(person_data$ENG_label == tenures4[4])
not_well <-  t.test(person_data$ENG_label == tenures4[5])
shares <- tibble(Tenure = c("Well", 
                            "N/A (less than 5 years old/speaks only English)", 
                            "Very well",
                            "Not at all",
                            "Not well"),
                 `Share` = c(well$estimate, 
                             lessthan5years_onlyspeakseng$estimate,
                             very_well$estimate,
                             not_at_all$estimate,
                             not_well$estimate),
                 Low = c(well$conf.int[1],
                         lessthan5years_onlyspeakseng$conf.int[1],
                         very_well$conf.int[1],
                         not_at_all$conf.int[1],
                         not_well$conf.int[1]),
                 High = c(well$conf.int[2],
                         lessthan5years_onlyspeakseng$conf.int[2],
                         very_well$conf.int[2],
                         not_at_all$conf.int[2],
                         not_well$conf.int[2]))
knitr::kable(shares, caption = "Proportions and 95-percent confidence intervals for ENG variable")
```

```{r}
tenures4 <- ggplot(shares, aes(x = Tenure, y = Share, ymin = Low, ymax = High)) +
  geom_bar(stat = "identity") +
  geom_errorbar(width = 0.5) +
  theme_bw() +
  scale_x_discrete(labels = c("Well", 
                            "N/A (less than 5 years old/speaks only English)", 
                            "Very well",
                            "Not at all",
                            "Not well")) +
  scale_y_continuous(name = "Share of population (error bars represent\n 95-percent confidence interval)",
                     breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     labels = c("0", "10%", "20%", "30%", "40%", "50%"))
```














