---
title: "Assignment5"
author: "Whytne Stevens"
date: "10/4/2020"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
library(wesanderson)
library(viridis)
library(jtools)
library(interactions)
library(knitr)
```





# Regression Models for PINCP Variable using the Detailed Household Language (HHLANP) variable for my categorical variables


Here I repeated the same processes as above but for my dataset that contained detailed information about the household languages. For my analysis, I'll be focusing on the HHLANP_labelMarathi category for all the models I'm running below

```{r load language data, results='hide'}
detailedlang <- read.csv("persondatalangdetail.csv") %>%
mutate(HHLANP_label = case_when(
    HHLANP_label=="English only household"~"1English only household",
    HHLANP_label=="Portuguese"~"Portuguese",
    HHLANP_label=="Other languages of Asia" ~ "Other languages of Asias",
    HHLANP_label=="Norwegian" ~ "Norwegian",
    HHLANP_label=="Spanish" ~ "Spanish",
    HHLANP_label=="Nepali"~"Nepali",
    HHLANP_label=="Mongolian" ~ "Mongolian",
    HHLANP_label=="Marathi" ~ "Marathi",
    HHLANP_label=="Mandarin" ~ "Mandarin",
    HHLANP_label=="Malayalam"~"Malayalam",
    HHLANP_label=="Khmer" ~ "Khmer",
    HHLANP_label=="Kannada" ~ "Kannada",
    HHLANP_label=="Igbo" ~ "Igbo",
    HHLANP_label=="Hungarian"~"Hungarian",
    HHLANP_label=="Hindi" ~ "Hindi",
    HHLANP_label=="Gujarati" ~ "Gujarati",
    HHLANP_label=="German" ~ "German",
    HHLANP_label=="French"~"French",
    HHLANP_label=="Farsi" ~ "Farsi",
    HHLANP_label=="Chinese" ~ "Chinese",
    HHLANP_label=="Bengali" ~ "Bengali",
    HHLANP_label=="Somali"~"Somali",
    HHLANP_label=="Swahili" ~ "Swahili",
    HHLANP_label=="Tagalog" ~ "Tagalog",
    HHLANP_label=="Tamil" ~ "Tamil",
    HHLANP_label=="Telugu"~"Telugu",
    HHLANP_label=="Thai" ~ "Thai",
    HHLANP_label=="Tigrinya" ~ "Tigrinya",
    HHLANP_label=="Urdu" ~ "Urdu",
    HHLANP_label=="Vietnamese" ~ "Vietnamese",
    HHLANP_label=="Yoruba" ~ "Yoruba",
    HHLANP_label=="Korean" ~ "Korean",
    HHLANP_label=="Amharic" ~ "Amharic",
    HHLANP_label=="Arabic" ~ "Arabic",
    HHLANP_label=="Burmese" ~ "Burmese",
    HHLANP_label=="Lao" ~ "Lao",
    HHLANP_label=="Other Mande languages" ~ "Other Mande languages",
    HHLANP_label=="Romanian" ~ "Romanian",
    HHLANP_label=="Russian" ~ "Russian"))

```






## Initial Regression Model for PINCP Variable using the Detailed Household Language (HHLANP) variable for my categorical variables and Results


```{r}
model5 <- lm(PINCP ~ HHLANP_label + WKHP + POVPIP, 
            data = detailedlang)
options(scipen = 999)
summary(model5)
```
This is the original regression model I ran in assignment 4 for this dataset. To restate the results from the last assignment, the multiple R-squared value for this model is 0.3352, meaning that it predicts about 34% of this model. When controlled for 'English only household,' people whose household language is under the 'Marathi' category make about $396,000 more in income than those in the other HHLANP categories. 



## Regression Model for PINCP Variable w/ log transformation for POVPIP variable, using the Detailed Household Language (HHLANP) variable for my categorical variables and Results
```{r}
model6 <- lm(PINCP ~ HHLANP_label + WKHP + log(POVPIP), 
            data = detailedlang)

summary(model6)
```
With this model the results differ somewhat from the initial model above. For example the multiple R-squared value for this model is 0.2964 (predicting about 30% of the model) while for the initial model it was 0.3352 (predicting about 34% of the model).  For people whose household language is under the 'Marathi' category, this model shows that they make about $400,000 more in income than those in the other HHLANP categories, in comparison to the initial model where that number was 396,000.Therefore there's only a 4,000 dollar difference in the models


## Regression Model for PINCP Variable w/ log transformation for WKHP variable, using the Detailed Household Language (HHLANP) variable for my categorical variables and Results
```{r}
model7 <- lm(PINCP ~ HHLANP_label + log(WKHP) + POVPIP, 
            data = detailedlang)

summary(model7)
```
For this model, the multiple R-squared value is 0.334 (predicting about 33% of the model) while for the initial model it was 0.3352 (predicting about 34% of the model).  For people whose household language is under the 'Marathi' category, this model shows that they make about $394,000 more in income than those in the other HHLANP categories, in comparison to the initial model where that number was 396,000.Therefore there's only a 2,000 dollar difference in the models

## Regression Model for PINCP Variable w/ interaction items, using the Detailed Household Language (HHLANP) variable for my categorical variables and Results
```{r}
model8 <- lm(PINCP ~ HHLANP_label + WKHP + log(POVPIP) +
               log(POVPIP):HHLANP_label + HHLANP_label:WKHP +
               WKHP:log(POVPIP), 
             data = detailedlang)

summary(model8)
```

For this model, the multiple R-squared value is 0.3552 (predicting about 36% of the model) while for the initial model it was 0.3352 (predicting about 34% of the model).  For people whose household language is under the 'Marathi' category, this model shows that they make about $399,000 more in income than those in the other HHLANP categories, in comparison to the initial model where that number was 396,000.Therefore there's only a 3,000 dollar difference in the models


## Model fit for Models 5-8 and Results

After running these models, I then plotted them below to see which one had the best fit for my dataset:


```{r}
ModelFit2 <- tibble(model = c(1, 2, 3, 4),
                   R_square = c(summary(model5)$adj.r.squared,
                                summary(model6)$adj.r.squared,
                                summary(model7)$adj.r.squared,
                                summary(model8)$adj.r.squared))

ggplot(ModelFit2, aes(x = model, y = R_square)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 4, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "Adjusted R-squared value") +
  theme_bw()
```


Based on the chart above it seems that my initial model was the best fit. I've also put the result in a table below. Since my initial model is the preferred model, I though it would be interesting to also compare it with second best fitting model, Model 7



```{r}
coeff_names2 <- c("Weekly work hours" = "WKHP",
                 "Income to Poverty Ratio" = "POVPIP",
                 "Houshold language is Marathi(compared to other categories of detailed household languages)" = 
                   "HHLANP_labelMarathi")

export_summs(model5, model5, model7, 
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial model", "Preferred model", "Second Best Model"),
             coefs = coeff_names2)
```

And finally, I created charts for both model5 and model7 to show the effect the Marathi category had on predicted income for the people included in my dataset

```{r}
coeff_desc <- c("Weekly work hours" = "WKHP",
                 "Income to Poverty Ratio" = "POVPIP",
                 "Houshold language is Marathi\n(compared to other categories \nof detailed household languages)" = 
                   "HHLANP_labelMarathi")

plot_coefs(model5, 
           coefs = coeff_desc,
           plot.distributions = TRUE,
           rescale.distributions = TRUE) +
  scale_x_continuous(name = "Effect on predicted income")
```


```{r}
coeff_desc <- c("Weekly work hours" = "WKHP",
                 "Income to Poverty Ratio" = "POVPIP",
                 "Houshold language is Marathi\n(compared to other categories \nof detailed household languages)" = 
                   "HHLANP_labelMarathi")

plot_coefs(model7, 
           coefs = coeff_desc,
           plot.distributions = TRUE,
           rescale.distributions = TRUE) +
  scale_x_continuous(name = "Effect on predicted income")
```


