---
title: "LowellMADemos"
author: "Whytne Stevens"
date: "2/28/2021"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

# Lowell, MA Demos
Below are the variables that could help us understand the urban design conditions on the ground:

- Class of Worker (COW) (categorical)

- Detailed Household Language (HHLANP) (categorical)

- Total Person's Income (PINCP) (continuous)

- Means of Transportation to Work (JWTRNS)

- Household/Family Type (includes cohabitation)(HHT2)

- Recoded Detailed Ancestry (ANC1P)

- Place of Birth (POBP)

- When Structure First Built (YBL)

- School Enrollment (SCH)

- Disability (DIS)

- Vision Difficulty (DEYE)

- Hearing Difficulty (DEAR)

- Self-care Difficulty (DDRS)

- Ambulatory (physical) Difficulty (DPHY)

- Cognitive Difficulty (DREM)

- Independent Living Difficulty (DOUT)

- Grandparents Responsible for Grandchildren (GCR)

- Presence of People 18 and under in Household (R18) 

- Presence of People 65 and older in Household (R65)

- Presence of Subfamilies in Household (PSF)

- Number of People in Household (NP)

- Presence of Non Relative in Household (NR)

- Number of People in Family (NPF)

- Lot Size (ACR)             

- Travel Time to Work (JWMNP) 

- Hours worked per week (WKHP) (continuous)

- Income to Poverty Ratio (POVPIP) (continuous)

- Adjustment factor for income and earnings dollar amounts (6 implied decimal places) (ADJINC)(Continuous)*

*used for PINCP Variable


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r load libraries}
library(ggplot2)
library(tidycensus)
library(ggthemes)
library(tidyverse)
```

```{r load person-level microdata variables}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```

```{r load ACS area variables}
area_vars_2018 <- load_variables(2018, "acs1")
```

```{r message=FALSE, results='hide'}
lowell <- c("00502")
```

```{r load person-level data, results= 'hide'}
lowelldemos <- get_pums(variables = c("JWTR",
                                      "HHT",
                                      "ANC1P",
                                      "POBP",
                                      "YBL", 
                                      "SCH", 
                                      "DIS",
                                      "DEYE",
                                      "DEAR",
                                      "DDRS",
                                      "DPHY",
                                      "DREM",
                                      "DOUT",
                                      "GCR",
                                      "R18", 
                                      "R65", 
                                      "PSF",
                                      "NP",
                                      "NR",
                                      "NPF",
                                      "ACR", 
                                      "JWMNP", 
                                      "COW",
                                      "SOCP",
                                      "LANP",
                                      "PINCP", 
                                      "WKHP", 
                                      "POVPIP",
                                      "ADJINC"),
                        state = "MA",
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>% 
  filter(PINCP > 0,
         WKHP > 0,
         POVPIP > 0) %>%
  select(JWTR_label, HHT_label, ANC1P_label, POBP_label, YBL_label, SCH_label, DIS_label, DEYE_label, DEAR_label, DDRS_label, DPHY_label, DREM_label, DOUT_label, GCR_label, R18_label, R65_label, PSF_label, NP, NR_label, NPF, ACR_label, JWMNP, COW_label, SOCP_label, LANP_label, PINCP, WKHP, POVPIP)
```

```{r load lowelldemos}
 head(lowelldemos, 1)
 tail(lowelldemos, 596)
```
## Saving Data
Lastly, I saved my data to a csv file:

```{r write_csv}
write_csv(lowelldemos, "lowelldemos.csv")
```

# Frequency Counts For Categorical Variables

```{r}
unique(lowelldemos$JWTR_label)
```

```{r}
table(lowelldemos$JWTR_label)
knitr::kable(table(lowelldemos$JWTR_label), caption = "Frequency Counts for JWTR Variable")
```

```{r}
unique(lowelldemos$HHT_label)
```

```{r}
table(lowelldemos$HHT_label)
knitr::kable(table(lowelldemos$HHT_label), caption = "Frequency Counts for HHT Variable")
```

```{r}
unique(lowelldemos$ANC1P_label)
```

```{r}
table(lowelldemos$ANC1P_label)
knitr::kable(table(lowelldemos$ANC1P_label), caption = "Frequency Counts for ANC1P Variable")
```

```{r}
unique(lowelldemos$POBP_label)
```

```{r}
table(lowelldemos$POBP_label)
knitr::kable(table(lowelldemos$POBP_label), caption = "Frequency Counts for POBP Variable")
```

```{r}
unique(lowelldemos$YBL_label)
```

```{r}
table(lowelldemos$YBL_label)
knitr::kable(table(lowelldemos$YBL_label), caption = "Frequency Counts for YBL Variable")
```

```{r}
unique(lowelldemos$SCH_label)
```

```{r}
table(lowelldemos$SCH_label)
knitr::kable(table(lowelldemos$SCH_label), caption = "Frequency Counts for SCH Variable")
```

```{r}
unique(lowelldemos$DIS_label)
```

```{r}
table(lowelldemos$DIS_label)
knitr::kable(table(lowelldemos$DIS_label), caption = "Frequency Counts for DIS Variable")
```

```{r}
unique(lowelldemos$DEYE_label)
```

```{r}
table(lowelldemos$DEYE_label)
knitr::kable(table(lowelldemos$DEYE_label), caption = "Frequency Counts for DEYE Variable")
```

```{r}
unique(lowelldemos$DEAR_label)
```

```{r}
table(lowelldemos$DEAR_label)
knitr::kable(table(lowelldemos$DEAR_label), caption = "Frequency Counts for DEAR Variable")
```

```{r}
unique(lowelldemos$DDRS_label)
```

```{r}
table(lowelldemos$DDRS_label)
knitr::kable(table(lowelldemos$DDRS_label), caption = "Frequency Counts for DDRS Variable")
```

```{r}
unique(lowelldemos$DPHY_label)
```

```{r}
table(lowelldemos$DPHY_label)
knitr::kable(table(lowelldemos$DPHY_label), caption = "Frequency Counts for DPHY Variable")
```

```{r}
unique(lowelldemos$DREM_label)
```

```{r}
table(lowelldemos$DREM_label)
knitr::kable(table(lowelldemos$DREM_label), caption = "Frequency Counts for DREM Variable")
```

```{r}
unique(lowelldemos$DOUT_label)
```

```{r}
table(lowelldemos$DOUT_label)
knitr::kable(table(lowelldemos$DOUT_label), caption = "Frequency Counts for DOUT Variable")
```

```{r}
unique(lowelldemos$GCR_label)
```

```{r}
table(lowelldemos$GCR_label)
knitr::kable(table(lowelldemos$GCR_label), caption = "Frequency Counts for GCR Variable")
```

```{r}
unique(lowelldemos$R18_label)
```

```{r}
table(lowelldemos$R18_label)
knitr::kable(table(lowelldemos$R18_label), caption = "Frequency Counts for R18 Variable")
```

```{r}
unique(lowelldemos$R65_label)
```

```{r}
table(lowelldemos$R65_label)
knitr::kable(table(lowelldemos$R65_label), caption = "Frequency Counts for R65 Variable")
```

```{r}
unique(lowelldemos$PSF_label)
```

```{r}
table(lowelldemos$PSF_label)
knitr::kable(table(lowelldemos$PSF_label), caption = "Frequency Counts for PSF Variable")
```

```{r}
unique(lowelldemos$NR_label)
```

```{r}
table(lowelldemos$NR_label)
knitr::kable(table(lowelldemos$NR5_label), caption = "Frequency Counts for NR Variable")
```

```{r}
unique(lowelldemos$ACR_label)
```

```{r}
table(lowelldemos$ACR_label)
knitr::kable(table(lowelldemos$ACR_label), caption = "Frequency Counts for ACR Variable")
```

```{r}
unique(lowelldemos$COW_label)
```

```{r}
table(lowelldemos$COW_label)
knitr::kable(table(lowelldemos$COW_label), caption = "Frequency Counts for COW Variable")
```

```{r}
unique(lowelldemos$SOCP_label)
```

```{r}
table(lowelldemos$SOCP_label)
knitr::kable(table(lowelldemos$SOCP_label), caption = "Frequency Counts for SOCP Variable")
```

```{r}
unique(lowelldemos$LANP_label)
```

```{r}
table(lowelldemos$LANP_label)
knitr::kable(table(lowelldemos$LANP_label), caption = "Frequency Counts for LANP Variable")
```





















































